\documentclass[12pt,a4paper]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{grey}
\moderncvicons{awesome}
\nopagenumbers{}
\usepackage{quattrocento}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{graphicx}
\usepackage[none]{hyphenat}
%\usepackage{fullpage}

\name{Joel}{Xavier Rocha}
\title{\small Brazilian. Date of birth: 12/28/89.}
\address{390, Alanis Maria Laurindo de Oliveira Avenue}{Fortaleza, Ceará. Brazil.}
\email{joelxr@gmail.com}
\homepage{joelxr.github.io}
\phone[mobile]{+55 85 99773.3473}
\phone[fixed]{+55 85 3259.2955}
\social[linkedin]{joelxr}
\social[twitter]{joelxr}
\social[github]{joelxr}
\begin{document}
\makecvtitle

\begin{itemize}
    \item Over six years of experience in Information Technology as a technical analyst, working with analysis and development of meaningful solutions.
    \item Valuable team asset, proactive profile and entrepreneur in search of new challenges and with great capacity to absorb and develop new technologies and ease of teamwork, focus on results, customer focus.
    \item Combined with technical leadership for the development area and strong analytical skills followed by knowledge in process and methods to develop and maintain software.
    \item With a solid base on Java/J2EE platform and environment, worked in many projects for the leading companies and institutes who support a large scale of daily operations.
\end{itemize}

\section{Education and Certifications}
\cventry{2008--2015}{Bachelor Degree}{Federal Institute of Education, Science and Technology of Ceará}{}{IFCE}{Computer Engineer}

\section{Courses and Certifications}

\cventry{2009}{Course}{iFactory Solutions}{}{}{WEB Development with Java}
\cventry{2010}{Course}{Foreign Language Center of the state of Ceará}{CLEC}{}{English}
\cventry{2017}{Course}{Udemy}{\httplink{ude.my/UC-I9OQPCKI}}{}{Complete Course for NodeJS and MongoDB Developer}
\cventry{2017}{Course}{Mongo DB University}{\httplink{goo.gl/WQy24D}}{}{MongoDB for Node.js Developers}
\cventry{2016}{Certification}{Oracle}{}{}{Java Standard Edition 6 Programmer}
\cventry{2018}{Certification}{ANBIMA}{}{}{CPA-20}

\section{Languages}
\cvdoubleitem{Portuguese}{Native}{English}{Advanced}
\cvdoubleitem{Spanish}{Intermediary}{Italian}{Basic}

\section{Skills}
\begin{itemize}
    \item \textbf{Back-end}
        \begin{itemize}
            \item Java:
                \begin{itemize}
                    \item JEE, JSP, EL, EJB, JSF, JPA, Android, JasperReports.
                    \item Frameworks: Spring VRaptor, Hibernate.
                    \item Testing: JUnit, Mockito, Powermock, Selenium.
                    \item Servers: IBM Websphere, Glassfish, Tomcat, JBoss, Wildfly.
                    \item Task Runners: Ant, Maven, Gradle.
                    \item Others: Sonar, PMD.
                \end{itemize}
            \item NodeJS: Express, npm.
            \item Ruby: RubyGems, RSpec, Ruby On Rails.
            \item C\#: .NET Framework 3.5.
            \item Relational Databases: Oracle, SQL Server, MySQL, SQLite.
            \item NoSQL: MongoDB.
        \end{itemize}
    \item \textbf{Front-end}
        \begin{itemize}
            \item HTML, Responsive WEB.
            \item CSS: Twitter's Bootstrap and Materialize CSS, SASS.
            \item JavaScript.
                \begin{itemize}
                    \item jQuery.
                    \item Task runners: npm scripts, Grunt.
                    \item Bundler: Browserify, Webpack.
                    \item Frameworks: AngularJS, VueJS.
                \end{itemize}
        \end{itemize}
    \item \textbf{Others}
        \begin{itemize}
            \item Banking technologies: Calypso, FIX Protocol.
            \item Version control system: Git, SVN and CVS.
            \item Continuous Integration: Jenkins and TravisCI.
            \item HTTP, HTTPS requests and SSH.
            \item Linux, Shellscript (BASH, ZSH).
            \item Text Editors and IDE: Eclipse, IntelliJ IDEA, Android Studio and Vim.
            \item \LaTeX\
        \end{itemize}
\end{itemize}

\section{Experience}

\cventry{Apr 2016 until now}{Municipal Bureau of Finance}{Technical Analyst}{}{}{}{Working to Municipal Bureau of Finance (aka. SEFIN), I'm contributing to develop projects that are able to handle all city incoming taxes, we work with Java solutions.\newline {}}

\cventry{Nov 2012 Apr 2016}{CPQi}{Technical Leader and Technical Analyst}{}{}{}{At CPQi, I have contributed to five solutions  developed to improve the Brazil and Chile financial markets. All these solutions were developed to banks and agencies which are strongly engaged in daily trades. Our clients have trusted their most important and valuable systems to us, to develop and support it.\newline{}}

\cventry{Nov 2010 Nov 2012}{Ebix}{Senior Developer}{}{}{}{I worked at the maintenance and development for the WEB systems of the leading insurance companies in Brazil. Mostly of these insurance systems were running in production or in pre production environment. To delivery correctly all the clients requirements, we made a strongly partnership with all the insurances team.\newline{}}

\cventry{Apr 2009 Nov 2010}{Usix}{Trainee}{}{}{}{I worked at the maintenance and development of WEB solutions. Initially, 20h per week then 30h per week. Working with Java and MVC and Command design patterns, some features we written in Java Script.\newline{}}

\cventry{Jul 2008\newline Apr 2009}{Artificial Intelligence Lab. Lambda}{Volunteer}{}{}{}{Developed a global monitoring system written in Ruby On Rails and Google Maps API. In this lab we had a lot of study cells, such as Java and Ruby.\newline{}}

\section{Hobbies}

\begin{itemize}
    \item Reading,
    \item Board Games,
    \item Coffee.
\end{itemize}

\end{document}
